---
title: "Archiving sets: artifacts, data and functions"
author: "Marcin Kosinski"
date: "September 14th, 2015"
output: rmarkdown::tufte_handout
vignette: >
  %\VignetteIndexEntry{Archiving Sets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


Let's prepare some set to be archived.

```{r}
library(ggplot2)
library(ggthemes)
library(archivist2)
createEmptyRepo( "SETS" )
```

```{r}
setLocalRepo( "SETS" )
data(iris)

plotArtifact <- ggplot( iris, aes(x = Sepal.Length, y = Species)) +
  geom_point()+
  theme_wsj()

plotData <- iris
plotFunctions <- list( ggplot, geom_point, theme_wsj)
```

Such set now can be archived using `saveSetToRepo` function

```{r}
saveSetToRepo( artifact = plotArtifact,
                           data = plotData,
                           functions = plotFunctions)
```


# Description

`saveSetToRepo` function saves desired set of artifacts to the local `Repository` in a given directory.
To learn more about artifacts visit [http://pbiecek.github.io/archivist/](http://pbiecek.github.io/archivist/). 
Set is a collection containing

- an artifact,
- data needed to create the artifact,
- list of functions needed to create the artifact.

# Details
`saveSetToRepo` archives `artifact`, `data` and `functions` using `saveToRepo` function but additionally it adds `Tags` to every part of a set in convention as: `set:md5hashOfArtifact` to remember
 that all objects came originally from one set. This additional tag helps to restore a set from a `Repository`.

# Value
 As a result of this function a character strings is returned, which determines
the `md5hash` of the archived artifact.


# Some technical solutions

`saveSetToRepo` uses `saveToRepo` function so normally names of elements of a set can not be archived as a `name` tag. The names of all archived elements from a set are archived under tag named `set:name:` .

## showLocalRepo

One can check archived elements that come only from sets.


```{r}
showLocalRepo(method = "sets")
```

## loadSetFromLocalRepo

Having a tag named `set:name` and a tag named `set` that specify to which artifacts this element is linked one can restore already archived set with `loadSetFromLocalRepo` function (not yet in the **archivist** package) by giving artifact's `md5hash` that is an output of a `saveSetToRepo` function.


```{r}
loadSetFromLocalRepo <- function( md5hash, repoDir = NULL ){
  
  stopifnot( is.character( md5hash ), length( md5hash ) == 1 )
  
  # get hashes
  artifactHash <- md5hash
  SetElementsHashes <- searchInLocalRepo( paste0("set:", md5hash ), fixed = FALSE,
                                          repoDir = repoDir) 
  
  # get names
  artifactName <- getTagsLocal( artifactHash, tag="set:name", repoDir = repoDir)
  artifactName <- sub(x = artifactName, pattern = "set:name:", replacement = "")
  
  SetElementsNames <- sapply( SetElementsHashes, function( element ){
    nameElem <- getTagsLocal( md5hash = element, tag="set:name", repoDir = repoDir)
    sub(x = nameElem, pattern = "set:name:", replacement = "")
  })
  
  
  # assign artifact
  assign( x = artifactName, value = loadFromLocalRepo(artifactHash, repoDir = repoDir, value = TRUE), 
          envir = parent.frame(1))
  # assign elements of a set
  for( i in seq_along(SetElementsNames)){
    assign( x = SetElementsNames[i], value = loadFromLocalRepo(SetElementsHashes[i], repoDir = repoDir, value = TRUE), 
            envir = parent.frame(1))
  }
  
}
```

# Example

For archived set, let's remove the set from global environment and then let's load a set from **Repository**


```{r}
ls()
```

```{r}
rm( list = c("plotData", "plotFunctions", "plotArtifact") )
ls()
```

```{r}
loadSetFromLocalRepo("f0745effbbedbf160243a154c6339574")
ls()
```


